### 2016-11-02 docs/ms_communitySynchrony.Rmd
adds overview section to ms

>>>>

OVERVIEW OF OUR APPROACH
------------------------
\textcolor{blue}{This paper has two related goals.
First, we want to refine previous theory on the drivers of species synchrony} [@Loreau2008a].
\textcolor{blue}{We do not develop new theory, but we do derive new quantitative predictions from previous theory that can be tested with empirical data.
With explicit predictions in hand, we can (i) test the generality of a relatively simple quantitative model and (ii) place our empirical results in a broader theoretical context.
Second, we want to use multispecies population models to run simulation experiments that allow us to quantify the relative influence of theoretical drivers of species synchrony.
With empirically-based simulations in hand, we can (i) determine the most important drivers of species synchrony in our focal grassland communities and (ii) compare simulation results to theoretical predictions.}

\textcolor{blue}{Note that throughout this paper we refer to ``synchrony'' as a continuous variable.
Dynamics can be more or less synchronous or asynchronous, but synchrony and asynchrony are not dichotomous states.
Thus, our goal is to determine which processes (environmental responses, demographic stochasticity, and interspecific interactions) most affect the value of community-wide species synchrony, regardless of whether those processes make synchrony increase or decrease.}
